Manuscript Draft\\ \vspace{2cm} What is long-distance dispersal? And a taxonomy of dispersal events

### 2016-06-26 Manuscript/MS- What is LDD.tex
Edits for Discussion.

Combining spatially-explicit references to the geographic population limits and the $N^b_e$ area extent helps avoiding some imprecision in setting distance thresholds to characterize LDD events. In addition the framework outlined in Table 1 bridges the combined demographic and genetic effects of LDD events.

>>>>

Combining spatially-explicit references to the geographic population limits and the $N^b_e$ area extent helps avoiding some imprecision in setting distance thresholds to characterize LDD events. In addition, the framework outlined in Table 1 bridges the combined demographic and genetic effects of LDD events. When methods available to assign frugivore taxa to the analyzed dispersal events, as in the study case with \textit{P. mahaleb}, a classification in the four categories of events is possible. The frugivore assemblage of \textit{P. mahaleb} is composed by a diversified set of animal species spanning a wide rage of body sizes, ca. 12-14000 g in weight. We might expect that this extreme variation translates in an ample pattern of foraging modes, movement distances, and fruit/seed processing \citep{Jordano:2000ft}. If the results for \textit{P. mahaleb} are generalizable to other disperser assemblages, it seems that the functional roles of frugivore species in terms of contributions to LDD events are structured in two distinct groups: small-bodied frugivores, with substantial contributions to SDD events and a crucial role for in-situ population recruitment, and large-bodied species with a disproportionate contribution to LDD events.
